---
title: "Week 10 Final Project Work"
author: "Wong Zi Xin"
date: "`r Sys.Date()`"
output: html_document
---

```{r, eval=TRUE,echo=TRUE}
install.packages("tidyverse")
library(tidyverse) 
main_data <- read_csv("YearXPassenger.csv")
```

```{r, eval=TRUE,echo=TRUE}
glimpse(main_data)
```

```{r, eval=TRUE,echo=TRUE}
library(ggplot2)

data <- data.frame(
  Year = c(2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020, 2021, 2022),
  Passengers = c(1940870998, 1957039604, 1993921773, 2090264018, 2200784362, 2353855648, 2538298567, 2687118655, 2781871120, 670004952, 916286346, 1993529416)
)

install.packages("scales")
library(scales)

ggplot(data, aes(x=Year, y=Passengers)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title="Yearly Number of Air Travel Passengers", x="Year", y="Number of Passengers") +
  scale_x_continuous(breaks = seq(min(data$Year), max(data$Year), by = 1)) +
  scale_y_continuous(labels = comma)
```

```{r, eval=TRUE,echo=TRUE}
library(ggplot2)

countries <- c("Austria", "Belgium", "Bulgaria", "Switzerland", "Cyprus", "Czech Republic", 
               "Germany", "Denmark", "Estonia", "Greece", "Spain", "Finland", "France", 
               "Croatia", "Hungary", "Ireland", "Iceland", "Italy", "Lithuania", "Luxembourg", 
               "Latvia", "Malta", "Netherlands", "Norway", "Poland", "Portugal", "Romania", 
               "Sweden", "Slovenia", "Slovakia")

passengers <- c(298932566, 321254798, 97534094, 517992316, 93822450, 147668980, 2064031685, 
                320542978, 26235153, 494633376, 2024500025, 191461837, 1549182646, 81337127, 
                122948405, 318348005, 60403135, 1421709674, 49761994, 33365620, 60567731, 
                55473084, 714548819, 395550066, 353061444, 444634543, 163884824, 354426755, 
                14827401, 21823522)

df <- data.frame(Country = countries, Number_of_Passengers = passengers)

ggplot(data = df, aes(x = reorder(Country, -Number_of_Passengers), y = Number_of_Passengers)) +
  geom_bar(stat = "identity", fill = "grey") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
   scale_y_continuous(labels = scales::comma) +
  labs(title = "Number of Passengers by Country", x = "Country", y = "Number of Passengers")

```

```{r, eval=TRUE,echo=TRUE}
library(ggplot2)

data <- data.frame(
  Country = c("AT", "BE", "BG", "CH", "CY", "CZ", "DE", "DK", "EE", "EL", "ES", 
              "FI", "FR", "HR", "HU", "IE", "IS", "IT", "LT", "LU", "LV", "MT", 
              "NL", "NO", "PL", "PT", "RO", "SE", "SI", "SK"),
  Passengers = c(298932566, 321254798, 97534094, 517992316, 93822450, 147668980, 
                 2064031685, 320542978, 26235153, 494633376, 2024500025, 191461837, 
                 1549182646, 81337127, 122948405, 318348005, 60403135, 1421709674, 
                 49761994, 3336520, 60567731, 55473084, 714548819, 395550066, 
                 353061444, 444634543, 163884824, 354426755, 14827401, 21823522)
)

ggplot(data, aes(x = reorder(Country, -Passengers), y = Passengers)) + 
  geom_bar(stat = "identity", fill = "grey") +
  theme_minimal() +
  labs(title="Number of Passengers by Country", x="Country", y="Number of Passengers") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(labels = scales::comma)
```

```{r, eval=TRUE,echo=TRUE}
library(tidyverse)

# Using read_csv to read the data
data <- read_csv("/Users/zixinwong/Desktop/NUS/Academics/CNM/NM2207/FinalProject/shinyfinalproject/EU27_passenger_data.csv")

# Clean the data
cleaned_data <- data %>%
  select(geo, TIME_PERIOD, OBS_VALUE) %>%          # Select required columns
  pivot_wider(names_from = TIME_PERIOD,            # Spread the data
              values_from = OBS_VALUE)

# Display cleaned data using tribble (optional)
cleaned_data_tribble <- as_tibble(cleaned_data)

# View the cleaned data
cleaned_data
```

library(shiny)
library(ggplot2)
library(plotly)
library(dplyr)
library(shinydashboard)
library(reshape2)
library(scales)

# Define UI
ui <- fluidPage(
  
  # App title
  titlePanel("Data Story: The Big Picture"),
  
  # Create tabs for different graphs
  tabsetPanel(
    tabPanel("Number of Passengers by Country",
             # Output: Plotly Barplot
             plotlyOutput(outputId = "barPlot1")
    ),
    tabPanel("Number of Passengers by Year",
             # Output: Plotly Barplot
             plotlyOutput(outputId = "barPlot2")
    ),
    tabPanel("Heatmap of Passengers",
             # Output: Heatmap
             plotOutput(outputId = "heatmap")
    )
  )
)

# Define server logic
server <- function(input, output) { 
  
  # Read the CSV data into data frames
  data_country <- read.csv("country_passengers.csv")
  data_year <- read.csv("year_passengers.csv")
  data_heatmap <- read.csv("heatmap.csv", skip = 1, header = TRUE)
  
  # Melt the heatmap data, reorder it in alphabetical order from top to bottom
  data_melted <- melt(data_heatmap, id.vars = "Country", variable.name = "Year", value.name = "Value")
  data_melted$Year <- gsub("^X", "", data_melted$Year)
  data_melted$Country <- factor(data_melted$Country, levels = rev(sort(unique(data_melted$Country))))
  
  # Render the first graph
  output$barPlot1 <- renderPlotly({
    
    # Create a ggplot object
    p <- ggplot(data_country, aes(x = Country, y = Number.of.Passengers, text = paste("Country: ", Country, "<br>Passengers: ", scales::comma(Number.of.Passengers)))) +
      geom_bar(stat = "identity", fill = "grey", color = "white") +
      labs(x = "Country", y = "Number of Passengers", title = "Number of Passengers by Country") +
      theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      scale_y_continuous(labels = scales::comma, breaks = seq(0, max(data_country$Number.of.Passengers), by = 200000000))  # Customize y-axis breaks
    
    # Convert ggplot object to a plotly object
    ggplotly(p, tooltip = "text")
    
  })
  
  # Render the second graph
  output$barPlot2 <- renderPlotly({
    
    # Create a ggplot object
    p <- ggplot(data_year, aes(x = Year, y = Number.of.Passengers, text = paste("Year: ", Year, "<br>Passengers: ", scales::comma(Number.of.Passengers)))) +
      geom_bar(stat = "identity", fill = "grey", color = "white") +
      labs(x = "Year", y = "Number of Passengers", title = "Number of Passengers by Year") +
      theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      scale_y_continuous(labels = scales::comma, breaks = seq(0, max(data_year$Number.of.Passengers), by = 100000000))  # Customize y-axis breaks
    
    # Convert ggplot object to a plotly object
    ggplotly(p, tooltip = "text")
    
  })
  
  # Render the heatmap
  output$heatmap <- renderPlot({
    ggplot(data_melted, aes(x = Year, y = Country, fill = Value)) + 
      geom_tile() + 
      scale_fill_gradient(low = "white", high = "red", labels = scales::comma) +
      theme_minimal() +
      labs(title = "Heatmap", x = "Year", y = "Country")
    
  })
  
}

# Create Shiny app
shinyApp(ui = ui, server = server)
